Understanding the impact of electronically-delivered parenting advice

### 2019-03-09 paper/cogsci2019/cogsci2019.Rmd
update participants info and e2 results

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software [@datavyu]. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
Each session's video was coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
Parental bids for joint attention were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of passive (coordinated??) JA episodes.

@@

There is a main effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids. There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.

@@

### Participants. 
`r nrow(d)` infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. [specific demo info]

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.

@@

```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
ms_lex <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="TTR") 
ttr_mean <- d%>% group_by(Condition)%>%
  summarise(mean=mean(TTR), sd=sd(TTR))

@@

multiplot(e2tokens, e2types, cols=2)
```

@@

>>>>

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software [@datavyu]. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
Each session's video was coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
Parental bids for joint attention were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of coordinated JA episodes.

@@

There is (was?) a main effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids. There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.

@@

lmer_data <- d %>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         TTR = as.numeric(TTR),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         video = as.factor(video))
```

### Participants. 
`r nrow(d)` infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty nine% of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly- educated, with reports of highest level of education ranging from completed high school (n = 0), some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 35) or declined to state (n = 14).

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.60,0.90] (p < 0.05) for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] (p < 0.05) for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] (p < 0.05) for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] (p < 0.05) for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] (p < 0.05) for total duration of coordinated JA episodes.

@@

Parents' child-directed speech was transcribed and processed in the same way as in Experiment 1.

## Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# Predicting lexical diversity based on experimental condition. 
modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
summary(modTTR)

modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
summary(modMTLD)

# predict word tokens
tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
summary(tokens_mod)

# predict word types
types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
summary(types_mod)
```

We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with a random intercept per video using lme4 [@lme4].
There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8) = 3.16, *p*<.05). 
There was no significant effect of age.
A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding no significant effects of of age or condition.

```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}

d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

# all at once, but there are NAs in SD cols ?
e2 <- d %>% group_by(Condition) %>%
  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
            types=mean(types), types.sd=sd(types),
            tokens = mean(tokens), tokens.sd=sd(tokens))

ms_lex <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="TTR") 
ttr_mean <- d%>% group_by(Condition)%>%
  summarise(mean=mean(TTR), sd=sd(TTR))

@@

multiplot(e2tokens, e2types, cols=2)
```
```{r, e2-effect-size, echo=F}
cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
```

## Joint Attention
```{r, e2ja-regressions, echo=F, include=F}
x<- load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))

lmer_data <- d %>%
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids),
         Video = as.factor(video))

# Total number of bids
bids_mod <- lmer(bids_tot ~ age * condition + (1 | video), data = lmer_data)
summary(bids_mod)

# Episodes of coordinated joint attention.
cja_mod <- lmer(cja ~ age * condition + (1 | video), data = lmer_data)
summary(cja_mod)

# Episodes of passive joint attention.
pja_mod <- lmer(pja ~ age * condition + (1 | video), data = lmer_data)
summary(pja_mod)

# Total duration of passive joint attention.
pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = lmer_data)
summary(pja_time_mod)

# Total duration of coordinated joint attention.
cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = lmer_data)
summary(cja_time_mod)
```

```{r e2ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 2."}

ms_bids <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="bids")

e2bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

e2tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

multiplot(e2bids, e2tja, cols=2)
```

```{r e2ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 2."}
ms_pja <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "pja")

e2pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

multiplot(e2pja, e2cja, cols=2)
```

@@

Similar to results in Experiment 1, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
There was a marginal effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of coordinated joint attention.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
However, there was a main effect of age on number of episodes of passive joint attention, duration of passive and coordinated joint attention, 
with the older children having fewer episodes of passive joint attention, shorter duration of passive joint attention, and longer duration of coordinated joint attention. 
These results suggest that children become more socially engaging in interactions with their caregivers as they develop.
